### 2019-02-18 sections/intuition.tex
Tasks are never done

%NOTE: depends on: editors
Users can continuously interact with tasks, they will never terminate. The event
send by a user leads to a new task that can always receive a new event.

The new task can either be the same task, but with a new value for the changed
editor, or the system can decide to move on to the next task.

The decision to move on to the next task is not taken by the task itself.
It is based on a calculation to determine the next tasks.
The step combinators in $t \Then e$ and $t \Next e$ pass the value of $t$ to the continuation $e$.
They both act like $t$ as long as the step is guarded.
Once it becomes unguarded, the task continues as $e\ v$, where $v$ is the observed value of $t$.
% The continuation $e$ is a function which calculates the next task or $\Fail$, signalling no continuation is present.
The task $t \Next e$ requires an input event $\Continue$ (Continue) in addition to the step being unguarded. % in order to step.

The step combinators give rise to a method of internal communication.
They represent data flow that \emph{follows} control flow.

% The intuition about sequential composition is to first do one thing, and once it is done, do some other thing.
% The notion of sequential composition exists in two forms: the external and the internal step.

>>>>

Tasks never terminate, they always keep reacting to events.
Editors can always be changed or cleared, and step combinators move on to new tasks.

In a step $t \Next e$, the decision to move on to e is taken by $\Next$, not by t.
The decision is based on a speculative evaluation of $e$.
The step combinators in $t \Then e$ and $t \Next e$ pass the value $v$ of $t$ to the continuation $e$.
Both steps act like $t$ as long as the step is guarded.
A step is guarded as long as the speculative evaluation $e\ v$ yields $\Fail$.
Once it becomes unguarded, the task continues as $e\ v$.
The task $t \Next e$ requires a continue event $\Continue$ in addition to the step being unguarded.
We designed speculative evaluation so that it does not have side effects.

The step combinators give rise to a method of internal communication:
They represent data flow that \emph{follows} control flow.
